% !TeX encoding = UTF-8 Unicode
% !TeX program = XeLaTeX
% !TeX spellcheck = XeLaTeX

% Author : Yifei Wang, pppppass
% Description : Matetials: Python Standard Library --- Seminar on Selected Tools Week 1

\documentclass[english]{../TeXTemplate/pkupaper}

\usepackage{lipsum}
\usepackage{essay-def}

\newcommand{\cuniversity}{}
\newcommand{\cthesisname}{Matetials: Python Standard Library --- Seminar on Selected Tools Week 1}
\newcommand{\titlemark}{Matetials: Python Standard Library}

\title{\titlemark}
\author{Yifei Wang\quad pppppass}
\date{Updated on February 26, 2018}

\begin{document}
\raggedright

\maketitle
\tableofcontents
\section{Brief introduction}
The main purpose of this speech is to introduce several commonly used Python library. The standard library to Python is like the Webster Dictionary to English. Though reading the official document is the most recommended way to familiarize oneself with the standard library, using \textbf{help()} or \textbf{dir()} is a rather convenient option. It can deal with the majority of the problems that we meet. 

\section{Resources}
The official document of Python Standard Library is provided \href{https://docs.python.org/3.6/library/index.html}{here}. The index is provided \href{https://docs.python.org/3.6/py-modindex.html}{here}.  \href{http://python.usyiyi.cn/translate/python_352/library/index.html}{Python标准库} is the Chinese version. \href{https://pymotw.com/3/index.html}{Python 3 Module of the week} is a strong complementary material besides the official document. You can also access to a bunch of useful information in \href{https://www.zhihu.com/question/22100190}{应该怎样系统的学习Python标准库}.

\section{Python Standard Library}
\input{chap/datetime}
\input{chap/math}
\input{chap/random}
\input{chap/serialization}
\input{chap/collections}
\input{chap/re}
\input{chap/itertools}

\subsection{\texttt{abc}}

The module \verb"abc" is introduced in \href{https://docs.python.org/3/library/abc.html}{\texttt{abc}} in Python Standard Library Reference. See \href{https://segmentfault.com/a/1190000007921371}{this article} and \href{https://www.jianshu.com/p/19ed49293168}{this article} for comprehensive explanation. Note that the usage in latter article is obsolete and may lead to errors.

\subsection{\texttt{decimal} and \texttt{fractions}}

The module \verb"decimal" and \verb"fractions" are introduced in \href{https://docs.python.org/3/library/decimal.html}{\texttt{decimal}} and \href{https://docs.python.org/3/library/fractions.html} in Python Standard Library Reference. Note that these two articles may be too detailed for first reading.

\subsection{\texttt{argparse}}

The module \verb"argparse" is introduced in \href{https://docs.python.org/3/library/argparse.html}{\texttt{argparse}} in Python Standard Library Reference. There are tons of options for this module, but simple skeleton can be found in the first example.

\subsection{\texttt{logging}}

The module \verb"logging" is introduced in \href{https://docs.python.org/3/library/logging.html}{\texttt{logging}} in Python Standard Library Reference. Note that \href{http://python.jobbole.com/86887/}{this article} provides an introduction.

\section{Assignment}
\begin{thmque}[Required]
String to Timestamp: If you get the date and time input by the costumer, like \hl{2015-1-21 9:01:30} and the time zone information, like \hl{UTC+5:00}, all of which are \texttt{string} objects. Please devise a program to transform these given information to timestamp. See \verb"Assignment/StandardLibrary-StringToTimestamp" for details.
\end{thmque}
\begin{thmque}
Timing Decorator: Devise a \hl{decorator}, which can affect any function and print the executing time of the function. See \verb"Assignment/StandardLibrary-TimingDecorator" for details.
\end{thmque}
\begin{thmque}[Required]
Stack: Use the \hl{deque} to realize a stack class. See \verb"Assignment/StandardLibrary-Stack" for details.
\end{thmque}
\begin{thmque}
Stack and JSON: Serialize an object from the stack class above to a \hl{\{\}} in JSON. See \verb"Assignment/StandardLibrary-StackJSON" for details.
\end{thmque}
\begin{thmque}[Required]
FIFO Dict: Use the \hl{OrderedDict} to realize a FIFO (first in first out) dict. When the dict is full, delete the Key added the ealiest. See \verb"Assignment/StandardLibrary-FIFODict" for details.
\end{thmque}
\begin{thmque}[Required]
EMail Address: Write a regular expression to examine Email address. It should examine \verb"someone@gmail.com" and \verb"bill.gates@microsoft.com". See \verb"Assignment/StandardLibrary-EMailAddress" for details.
\end{thmque}
\begin{thmque}
EMail Name: Write a regular expression to examine Email address and get the name in it. For example, \verb"<Tom Paris> tom@voyager.org" $\implies$ \verb"Tom Paris", \verb"bob@example.com" $\implies$ \verb"bob". See \verb"Assignment/StandardLibrary-EMailName" for details.
\end{thmque}
\begin{thmque}
$\pi$: Use the \verb"itertools.count" to calculate the value of $\pi$, using the formula
\begin{equation}
\frac{\pi}{4} = \sum_{i=0}^{\infty}{ \frac{(-1)^n }{ 2 n + 1 } }.
\end{equation}
\end{thmque}
\begin{thmque}
Abstract Base Class: Implement an abstract base class \verb"AbstractBaseClass", from which \verb"DerivedClass" is derived. See \verb"Assignment/StandardLibrary-AbstractBaseClass" for details.
\end{thmque}
\begin{thmque}
Data Loader: Use \verb"random.shuffle" to construct a class \verb"DataLoader" for SGD. See \verb"Assignment/StandardLibrary-DataLoader" for details.
\end{thmque}
\begin{thmque}
Numbers: Use \verb"decimal" and \verb"fractions" module to accomplish two high precision tasks. See \verb"Assignment/StandardLibrary-Numbers" for details.
\end{thmque}
\begin{thmque}
Implement \verb"prog.py" in the first code block in \href{https://docs.python.org/3/library/argparse.html}{argparse} in Python Standard Library Reference.
\end{thmque}
\begin{thmque}
Implement the first example about \verb"logging" module in \href{http://python.jobbole.com/86887/}{this article}.
\end{thmque}
\end{document}
